\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{CAS 741: Problem Statement\\Truss}

\author{Ting-Yu Wu}

\date{\today}

\input{../Comments}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 21, 2020 & Ting-Yu Wu & Initial Draft\\
September 27, 2020 & Ting-Yu Wu & Updates according to issue \#1\\
\bottomrule
\end{tabularx}
\end{table}

\section*{Problem}
A truss is a framework that could hold something up, supporting bridges, roofs, 
or other structures. This project will focus on solving truss bridge problems. 
Before operating a bridge, there are lots of testing and evaluations need to be 
done, one of them is an analysis of trusses. We are trying to figure out 
whether a bridge is safe enough to support various loads it encounters (e.g., 
the weight of vehicles crossing it) by analyzing the stresses and unknown 
forces acting in truss members. Knowing both motions and forces within the 
trusses prepares us for a better understanding of how stable the architecture 
is. The inputs of the software are the structures of the bridge, external 
forces, and load forces. The outputs are all the internal forces of truss 
members and the stress distribution (tension and compression)\\

The software will implement the Drasil project. Following is the homepage of 
Drasil: https://github.com/JacquesCarette/Drasil/.

\section*{Context}
Specific stakeholders include students, professors, researchers in the field of 
mechanical and civil engineering, individuals interested in solving truss 
problems, and all contributors to the Drasil project. The software is 
compatible with various operating system environments, including Windows, 
Linux, and MacOS.

\end{document}